Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-06-19 appendix.tex
Tweaks to appendix

\begin{equation}
\tilde{Q_0} = \sum_{i=0}^{r-1} q_i
\end{equation}

is not, in general, equal to $Q_0$.  We can retain conservation by
adding the factor $(Q_0 - \tilde{Q_0})/r$ to the interpolated values
(or by multiplying the interpolated values by the ratio
$Q_0/\tilde{Q_0}$).  Unfortunately, the result of this procedure does
not preserve monotonicity -- it can introduce local minima and maxima
at at parent cell boundaries.  We can then attempt to correct that by
taking a weighted average between the interpolated values on the
subgrid and the parent value with weights computed such that the
interpolated values at the edge of the parent cell are not local
maxima compared to the interpolated values in the neighboring parent
cell.

>>>>

\begin{equation}
\tilde{Q_0} = \sum_{i=0}^{r-1} q_i
\end{equation}
is not, in general, equal to $Q_0$.  We can retain conservation by
adding the factor $(Q_0 - \tilde{Q_0})/r$ to the interpolated values
(or by multiplying the interpolated values by the ratio
$Q_0/\tilde{Q_0}$).  Unfortunately, the result of this procedure does
not preserve monotonicity -- it can introduce local minima and maxima
at parent cell boundaries.  We can then attempt to correct that by
taking a weighted average between the interpolated values on the
subgrid and the parent value with weights computed such that the
interpolated values at the edge of the parent cell are not local
maxima compared to the interpolated values in the neighboring parent
cell.
